Spatial distribution of environmental DNA in a nearshore marine habitat

### 2016-11-16 Manuscript/v1.0_PeerJ/carkeek_grid.tex
comment out TODOs, fix much less than symbol

@@

%-----------------------------------NOTES---------------------------------------

@@

\subsubsection*{Diversity in Space}
Sites offshore tend to be less diverse (richness) and more even (1-Simpson's D) than those inshore (Figure \ref{diversity_distance}). Mean OTU richness declined by 1.42 per 1000 meters from a mean of 17.6 taxa (95\%CI = 2.15) inshore to 11.9 taxa (95\%CI = 4.31) at offshore locations (p = 0.0415; Fig. figures/diversity.pdf). 1-Simpson's diversity, the probability that two reads chosen at random from a sample belong to different species, increased by .0666 per 1000 meters from 0.225 (95\%CI = 0.0558) to 0.491 (95\%CI = $\pm$ 0.112), indicating that sequence reads were less evenly distributed among taxa in offshore samples (p <<< 0.05; Figure \ref{diversity_distance}). There was no evidence for spatial autocorrelation for any of the diversity metrics (Moran's I, p > 0.05; Figure \ref{diversity}).

@@

\subsection{Sequence Data}
\label{sequence_data}
All sequence files and metadata are available from EMBL:\\ \verb!http://www.ebi.ac.uk/ena/data/view/TODO! \\
(TODO SUBMIT DATA AND METADATA; ADD URL)

\subsection{Project Repository}
The following components are available from the project repository on GitHub: \\
\verb!https://github.com/jimmyodonnell/Carkeek_eDNA_grid!\\
(TODO INSERT DOI FROM FINAL COMMIT BEFORE PUBLICATION)

>>>>

%-----------------------------------NOTES---------------------------------------
% (TODO SUBMIT DATA AND METADATA; ADD URL)
% (TODO INSERT DOI FROM FINAL COMMIT BEFORE PUBLICATION)

@@

@@

\subsubsection*{Diversity in Space}
Sites offshore tend to be less diverse (richness) and more even (1-Simpson's D) than those inshore (Figure \ref{diversity_distance}). Mean OTU richness declined by 1.42 per 1000 meters from a mean of 17.6 taxa (95\%CI = 2.15) inshore to 11.9 taxa (95\%CI = 4.31) at offshore locations (p = 0.0415; Fig. figures/diversity.pdf). 1-Simpson's diversity, the probability that two reads chosen at random from a sample belong to different species, increased by .0666 per 1000 meters from 0.225 (95\%CI = 0.0558) to 0.491 (95\%CI = $\pm$ 0.112), indicating that sequence reads were less evenly distributed among taxa in offshore samples (p $\ll$ 0.05; Figure \ref{diversity_distance}). There was no evidence for spatial autocorrelation for any of the diversity metrics (Moran's I, p > 0.05; Figure \ref{diversity}).

@@

\subsection{Sequence Data}
\label{sequence_data}
All sequence files and metadata are available from EMBL:\\ \verb!http://www.ebi.ac.uk/ena/data/view/FIXME! \\

\subsection{Project Repository}
The following components are available from the project repository on GitHub: \\
\verb!https://github.com/jimmyodonnell/Carkeek_eDNA_grid!\\
\verb!http://dx.doi.org/FIXME!\\
